Figures

### 2020-03-26 manuscript/figures.Rmd
rm hypenation

![Diagram showing the assumption of most lake depth models that the nearshore slope extends into the lake and that all lakes have a common relationship between nearshore and in-lake slope. ](../figures/slope_diagram.pdf){width=75%}

>>>>

![Diagram showing the assumption of most lake depth models that the nearshore slope extends into the lake and that all lakes have a common relationship between nearshore and inlake slope. ](../figures/slope_diagram.pdf){width=75%}
